Fractional Decomposition Trees: A tool for studying mixed-integer-program integrality gaps

### 2018-11-21 IPCO format/FDT.tex
Abstract update

%
\authorrunning{R. Carr, A. Haddadan, C. Phillips}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
% Shorter institutions
\institute{University of New Mexico, \email{bobcarr@unm.}\\   \and
Carnegie Mellon University, \email{ahaddada@cmu.edu}\and
Sandia National Laboratories, \email{caphill@sandia.gov}}
% Longer version
%\institute{University of New Mexico, Albuquerque NM 87131, USA\\
%\email{bobcarr@unm.}\\   \and
%Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
%\email{ahaddada@cmu.edu}\and
%Sandia National Laboratories, Albuquerque, NM 87185, USA\\
%\email{caphill@sandia.gov}}
%
\maketitle              % typeset the header of the con	tribution
%
\begin{abstract}
We present a new algorithm for finding a feasible solution for a mixed-integer linear program. The algorithm runs in polynomial time and is guaranteed to find a feasible integer solution provided the
integrality gap is bounded. The algorithm is based on convex decomposition of scaled linear-
programming relaxations, so in general it provides a suite of integer solutions. Because of the
relationship between convex decomposition and integrality gaps, this algorithm can be seen as an approximation algorithm. We apply our algorithm our algorithm to a class of 
fractional extreme points for two known problems in combinatorial optimization: the 2-edge-connected spanning subgraph problem and the tree augmentation problem. These computational experiments show that our algorithm can be used as a tool to evaluate the integrality gap of integer programs with their linear relaxation. Finally we provide a stronger characterization of integrality gap for a class of covering problems than that of \cite{goemans}.

>>>>

%
\authorrunning{R. Carr, A. Haddadan, C. Phillips}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
% Shorter institutions
\institute{University of New Mexico, \email{bobcarr@unm.}\\   \and
Carnegie Mellon University, \email{ahaddada@cmu.edu}\and
Sandia National Laboratories, \email{caphill@sandia.gov}}
% Longer version
%\institute{University of New Mexico, Albuquerque NM 87131, USA\\
%\email{bobcarr@unm.}\\   \and
%Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
%\email{ahaddada@cmu.edu}\and
%Sandia National Laboratories, Albuquerque, NM 87185, USA\\
%\email{caphill@sandia.gov}}
%
\maketitle              % typeset the header of the con	tribution
%
\begin{abstract}
We present a new algorithm/tool for studying integrality gaps of mixed-integer linear programming formulations.
The algorithm is based on convex decomposition of scaled linear-programming relaxations. The relationship between convex decomposition and integrality gaps provides both integrality-gap information and approximate solutions. 
% The algorithm finds a feasible solution for a mixed-integer linear program.
Our algorithm runs in polynomial time and is guaranteed to find a feasible integer solution provided the
integrality gap is bounded.  Thus when the algorithm fails, it proves an unbounded integrality gap.  The algorithm also provides a lower
bound on the instance integrality gap at each step. 
% so in general it provides a suite of integer solutions.
%, this algorithm can be seen as an approximation algorithm. 
We apply our algorithm to a class of 
fractional extreme points for two traveling-salesman-like problems: 2-edge-connected spanning subgraph (2EC) and tree augmentation.
These experiments provide insight into the current gap bounds.  Furthermore, for 2EC, the approximate solutions are consistently better than the best previous
approximation algorithm due to Christofides.
%These computational experiments show that our algorithm can be used as a tool to evaluate the integrality gap of integer programs with their linear relaxation.
% Finally we provide a stronger characterization of integrality gap for a class of covering problems than that of \cite{goemans}.
